---
title: "LMwithPred"
author: "Maria Cabanillas"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  
This is the linear model with prediction problem. Predict strength scores using data from the following web site

$H_0$ The null hypothesis is there is no difference in these models.  
$H_A$ There is a difference in the models when they are predicting the strength in the GRIP and ARM. 

```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require (ggplot)
```
###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)

```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() +  geom_smooth(method=lm)
```

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,New,interval="prediction")
```

###Plot scatterplot

```{r}
plot(SIMS~GRIP,data=data)

```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() +  geom_smooth(method=lm)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict.lm(model.1,New,interval="prediction")
```

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict.lm(model.1,New,interval="prediction")
```

```{r}
anova(model.1,model.3)
```
Based on the p value we reject the null hypothesis and conclude as we saw with the adjusted r-square that model 2 is a better predictor than model 1.